{Parallel Implementation of Time Series Analysis in Distributed Database Systems}

### 2013-10-05 draft.tex
intro & references

\title{Implementation of Parallel Algorithms for ARIMA in Distributed
  Database Systems}

@@

{\bf keywords}: distributive, parallel computation, database, machine
learning, big data, ARIMA

@@

% Introduce to MADlib, and implement ARIMA in MADlib
MADlib~\cite{madlib} is an open source library for scalable
in-database analytics, currently backed by the Predictive Analytics
Team at Pivotal Inc. It provides data-parallel implementations of
mathematical, statistical and machine-learning methods for structured
and unstructured data.

Time series analyses are important in econometrics, mathematical
finance, weather forecasting, earthquake prediction and many other
fields. For example, one of the most conspicuous data analytics task,
stock price forecasting, falls into the category of time series
analysis.

However, different from other common data analytics tasks, time series
data have a natural temporal ordering. And many time series modeling
methods, such as ARIMA~\cite{arima} and Cox proportional
hazards~\cite{cox}, therefore depend on sequential processing of time
series data, which raises a challenge for the data-parallel
implementation in MADlib.

In MADlib, we attack this challenge using an idea illustrated below
[TODO add a simple figure to compare MADlib ARIMA and order aggregate
with iterations].

@@

\begin{figure}[ht]
  \begin{centering}
    \includegraphics[scale=0.25]{sequential_vs_distributed.png}
  \end{centering}
  \caption{\label{fig:seq_vs_dist} The comparison between sequential
    and distributed designs. }
\end{figure}

>>>>

\title{{Parallel Implementation of Time Series Analysis in Distributed Database Systems}}

@@

{\bf keywords}: parallel computation, time series, database management system, machine learning, big data, ARIMA

@@

% Introduce to MADlib
MADlib~\cite{madlib} is an open source library for scalable
in-database analytics, currently backed by the Predictive Analytics
Team at Pivotal Inc. It provides data-parallel implementations of
mathematical, statistical and machine-learning methods for structured
and unstructured data.

% time series analysis is important
Time series analyses are important in econometrics, mathematical
finance, weather forecasting, earthquake prediction and many other
fields. For example, one of the most conspicuous data analytics task,
stock price forecasting, falls into the category of time series
analysis.
% time series analysis is hard to parallelize
However, different from other common data analytics tasks, time series
data have a natural temporal ordering. And many time series modeling
methods, such as ARIMA~\cite{arima} and Cox proportional
hazards~\cite{cox}, therefore depend on sequential processing of time
series data, which raises a challenge for the data-parallel
implementation in MADlib.

% we focus on ARIMA in this paper
In this paper, we present our parallel implementation of autoregressive integrated moving average (ARIMA), an popular and important time series analysis model, in MADlib.
% our idea is chunking
In MADlib, we attack this mismatch by taking advantage of the iterative nature of the learning algorithms and rely on only local ordering, illustrated in Fig. (\ref{fig:seq_vs_dist}).
\begin{figure}[ht]
  \begin{centering}
    \includegraphics[width=\textwidth]{sequential_vs_distributed.png}
  \end{centering}
  \caption{\label{fig:seq_vs_dist} The comparison between sequential
    and distributed designs. A segment is a running process in parallel databases.}
\end{figure}

@@
